Sequence Labeling for Gait Analysis using LSTM

### 2015-05-09 paper/paper.tex
Minor fixes

\section{Data}
\label{sec:Data}
Our training and testing was conducted on data from 10 healthy subjects walking 
on a treadmill at three different speeds for 50 seconds. Each sequence of 50 seconds is called a trial. This amounts to a total of 1500 seconds of recorded data, which roughly correspond to 1000 gait cycles.  For each subject, 3D motion capture data was collected using 18 reflective markers placed at precise body locations.%
\footnote
{
    The locations used were toe, ankle, heel, knee, greater trochanter (hip), tibia, femur, and anterior and posterior superior illiac spine (pelvis) on each leg.
}
The sampling frequency of this data is 100Hz. The event labels (target) were computed from ground force reaction data from force sensors embedded in the treadmill 
which is considered the gold standard in the field. 
In order to compute events the ground reaction forces in gravity's axis are thresholded at 20N; whenever the forces exceed this threshold, the foot is considered to be on the ground (stance). By searching for the transitions between stance and no-stance, the events are found.
The sampling frequency of this data is 1kHz.

@@

Before using it in our network we pre-processed the data as follows:
\begin{enumerate}
 \item Data was translated so that the mid-hip position (average position of the left and right hip markers) is located at $(0,0,0)$ at all times.
 \item Data was rotated so that gravity is aligned with the $z$ axis (was already the case) and the $x$ axis is aligned with the vector going from the left hip marker to the right hip marker, projected onto a plane orthogonal to $z$. The $y$ axis is defined as the direction orthogonal to $x$ and $y$. This allows the data to be independent of walking direction and the absolute reference frame in which the data was captured.
 \item Data for each marker was standardized.
\end{enumerate}

>>>>

\section{Data}
\label{sec:Data}

\subsection{Collection}
\label{sub:Collection}

Our training and testing was conducted on data from 10 healthy subjects walking 
on a treadmill at three different speeds for 50 seconds. Each sequence of 50 seconds is called a trial. This amounts to a total of 1500 seconds of recorded data, which roughly correspond to 1000 gait cycles.  For each subject, 3D motion capture data was collected using 18 reflective markers placed at precise body locations.%
\footnote
{
    The locations used were toe, ankle, heel, knee, greater trochanter (hip), tibia, femur, and anterior and posterior superior illiac spine (pelvis) on each leg.
}
The sampling frequency of this data is 100Hz. The event labels (target) were computed from ground force reaction data from force sensors embedded in the treadmill 
which is considered the gold standard in the field. 
In order to compute events the ground reaction forces in gravity's axis are thresholded at 20N; whenever the forces exceed this threshold, the foot is considered to be on the ground (stance). By searching for the transitions between stance and no-stance, the events are found.
The sampling frequency of this data is 1kHz.

\subsection{Test/Training Split}
\label{sub:Test/Training Split}

@@

\subsection{Preprocessing}
\label{sub:Preprocessing}

We used the following preprocessing steps:
\begin{enumerate}
 \item The data was translated so that the mid-hip position (average position of the left and right hip markers) is located at $(0,0,0)$ at all times.
 \item The data was rotated so that gravity is aligned with the $z$ axis (was already the case) and the $x$ axis is aligned with the vector going from the left hip marker to the right hip marker, projected onto a plane orthogonal to $z$. The $y$ axis is defined as the direction orthogonal to $x$ and $y$. This allows the data to be independent of walking direction and the absolute reference frame in which the data was captured.
 \item The data for each marker was standardized.
\end{enumerate}
